Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in 3 areas}

### 2021-09-21 paper/main.tex
slide show content

\title{Earth at night*\\
{\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}
}

@@

\begin{itemize}
    \item Lambda: 20\$
    \item EC2:20\$
    \item RDS:10\$
    \item NAT:10\$
\end{itemize}

@@

\textbf{Writing contribution includs:} The previous 8 paragraphs of solution summary, and F, G, H, I, J 
    subsections in it. The A, E, G subsections of proposed solution. The section of security 
    Considerations. The section of actual AWS expenditure.

>>>>

\title{Earth at night*\\
{\footnotesize \textsuperscript{*}The visualisation of average radiance in 3 areas}
}

@@

\begin{itemize}
    \item Lambda: 20\$
    \item EC2: 20\$
    \item RDS: 10\$
    \item NAT: 10\$
\end{itemize}

@@

\textbf{Writing contribution includs:} The previous 7 paragraphs of solution summary, and F, G, H, I, J 
    subsections in it. The A, E, G subsections of proposed solution. The section of security 
    Considerations. The section of actual AWS expenditure.
